\Large {\bf Protocol-Guided Analysis of Post-silicon Traces Under Limited Observability}

### 2015-12-28 paper.tex
Done minor edits

Post-silicon validation is performed by debuggers with deep
knowledge about the system's architecture and
microarchitecture, and the test environment.  Two key
insights are (1) the maximal number of instances of a flow
activated in the test environment, and (2)~the mutual
relationship between two flows.  For example, the test
environment may not permit multiple instances of firmware
authentication to operate concurrently, or a flow involving
audio and Web browsing to initiate until the flows
participating in boot are completed.  Our framework permits
incorporating such insights as constraints in trace
analysis; flow execution scenarios that violate these
constraints are ignored.  \textcolor{red}{These insights can lead to two advantages.
First, they help to reduce the potentially large number of partial
scenarios generated during the trace interpretation step, thus making 
the analysis more efficient.  Second, they permit the debugger
to quickly filter out uninteresting combinations of flows and focus on interesting
interleavings.}

This approach can be flexible in that it allows a debugger
to analyze the observed traces in a trail-and-error manner
if the precise knowledge of the system (micro-)architecture
is hard to come by.  For instance, the debugger might
initially make a very restricted assumption on how the SUD
executes a flow specification, and these assumptions can
potentially lead to an empty set of flow execution
scenarios.  Depending on which of these assumptions
triggered during the trace interpretation step, the debugger
can study these assumptions more carefully, and relax some
or all of them for the next run of analysis.  This iteration
can be repeated as many times as necessary until some
results deemed meaningful are produced.

@@

In order to find out the efficiency of the trace analysis
method for more realistic examples, in the case study
described in this section, a more detailed transaction level
model of a SoC is constructed within the GEM5
environment~\cite{Binkert2011}.  This SoC model, as shown in Fig.~\ref{SoC},
consists of
two ARM Cortex-A9 cores, each of which contains two separate
16KB data and instruction caches.  The caches are connected
to a 1GB memory through a memory bus model.

In this model, components communicate with each other by
sending and receiving various request and response messages.
In order to observe and trace communications occurring
inside this model during execution, monitors are attached to
links connecting the components. These monitors record the
messages flowing through the links they are attached to, and
store them into output trace files.

@@

For this model, we consider the flow specifications
describing the cache coherence protocols supported in GEM5\footnote{The GEM5 cache
  coherence protocols can be found at
  \url{http://www.gem5.org/docs/html/gem5MemorySystem.html}.}
that is used to build the model in Fig~\ref{SoC}.  These
flow specifications describe data/instruction read
operations and data write operations initiated from CPUs.
Three such flows describe the cache coherent protocols for
each CPU.  As there are two CPUs in this model, there are
actually six such flows considered for this model.

>>>>

Post-silicon validation is performed by debuggers with deep
knowledge about the system's architecture and
microarchitecture, and the test environment.  Two key
insights are (1) the maximal number of instances of a flow
activated in the test environment, and (2)~the mutual
relationship between two flows.  For example, the test
environment may not permit multiple instances of firmware
authentication to operate concurrently, or a flow involving
audio and Web browsing to initiate until the flows
participating in boot are completed.  Our framework permits
incorporating such insights as constraints in trace
analysis; flow execution scenarios that violate these
constraints are ignored.  These insights can lead to two
advantages.  First, they help to reduce the potentially
large number of partial scenarios generated during the trace
interpretation step, thus making the analysis more
efficient.  Second, they permit the debugger to quickly
filter out uninteresting combinations of flows and focus on
interesting interleavings.

This approach can be flexible in that it allows a debugger
to analyze the observed traces in a trial-and-error manner
if the precise knowledge of the system (micro-)architecture
is hard to come by.  For instance, the debugger might
initially make a very restricted assumption on how the SUD
executes a flow specification, and these assumptions can
potentially lead to an empty set of flow execution
scenarios.  Depending on which of these assumptions
triggered during the trace interpretation step, the debugger
can study these assumptions more carefully, and relax some
or all of them for the next run of analysis.  This iteration
can be repeated as many times as necessary until some
results deemed meaningful are produced.

@@

To determine the efficiency of the trace analysis method for
a realistic example, a transaction level model of a SoC is
constructed within the GEM5 environment~\cite{Binkert2011}.
This SoC model, as shown in Fig.~\ref{SoC}, consists of two
ARM Cortex-A9 cores, each of which contains two separate
16KB data and instruction caches.  The caches are connected
to a 1GB memory through a memory bus model.  Components
communicate with each other by sending and receiving various
request and response messages.  In order to observe and
trace communications occurring inside this model during
execution, monitors are attached to links connecting the
components.  These monitors record the messages flowing
through the links they are attached to, and store them into
output trace files.

@@

For this model, we consider the flow specifications
describing the cache coherence protocols supported in
GEM5\footnote{The GEM5 cache coherence protocols can be
  found at
  \url{http://www.gem5.org/docs/html/gem5MemorySystem.html}.}
that is used to build the model in Fig~\ref{SoC}.  These
flow specifications describe data/instruction read
operations and data write operations initiated from CPUs.
Three such flows describe the cache coherent protocols for
each CPU.  Since there are two CPUs, there are six flows in
the model.
